---
title: 'Totales Torrance'
subtitle: 'Correlaciones por Pares'
author: 'Ma Fernanda Serrano'
date: 2022-09-06
tags: ['totales', 'diagrama de columnas', 'corelaciones por pares', 'Fer Serrano', 'Torrance']
toc: TRUE
toc_depth: 3
output: hugodown::md_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
#source('https://github.com/umontano/CBQ_comandos_SPSS_lab_ChyC/raw/main/correlation_graphics.R')
source('https://github.com/umontano/CBQ_comandos_SPSS_lab_ChyC/raw/main/CBQ_comandosSPSS_lab_CHyC.R')
source('https://github.com/umontano/CBQ_comandos_SPSS_lab_ChyC/raw/main/correlation_graphics.R')
#source('/a/CBQ_comandos_SPSS_lab_ChyC/correlation_graphics.R')
```

```{r, include=FALSE, echo=FALSE}

library('tidytext')
library('widyr')
library('ggplot2')
library('dplyr')
library('tidyr')
library('tibble')
library('psych')
col_graphic_paired_significant_corrs <- function(columns_dataset, sign=0.05)
{

merged_dataset <- factors %>%
	add_id_column_numero %>%
	merge(add_id_column_numero(scales), by='numero') %>%
	merge(add_id_column_numero(raven), by='numero') %>%
	merge(add_id_column_numero(columns_dataset), by='numero') %>%
	mutate(numero=as.numeric(numero)) %>%
	select(!starts_with('X')) %>%
	select(where(is.numeric))

tor <- merged_dataset %>%
    select(c(names(columns_dataset), -numero))
torrest <- merged_dataset %>%
    select(-numero) %>%
    select(!names(columns_dataset))

#call scaterplots
corr_graph_scatters_list <- scatterplot_significant_correlations(tor, torrest, sign=sign)

	pmat <- corr.test(torrest, tor)$p
	cor_test_mat <- pmat
	rmat <- cor(torrest, tor)
	rmat[pmat > sign] <- NA
	rmat[abs(rmat) < 0.20] <- NA

    gpairs_by_others <- rmat %>%
		data.frame %>%
		mutate(item1=rownames(.)) %>%
		pivot_longer(!item1, names_to='item2', values_to='correlation') %>%
		filter(! is.na(correlation)) %>%
		mutate(item2=reorder_within(item2, correlation, item1)) %>%
		#mutate(item2=gsub('___.+', '', item2, perl=T)) %>%
		ggplot(aes(correlation, item2)) + 
		geom_col() +
		scale_y_reordered() +
		facet_wrap(~item1, scale='free_y')



    gpairs_by_columns_dataset <- rmat %>%
		data.frame %>%
		mutate(item2=rownames(.)) %>%
		pivot_longer(!item2, names_to='item1', values_to='correlation') %>%
		filter(! is.na(correlation)) %>%
		mutate(item2=reorder_within(item2, correlation, item1)) %>%
		#mutate(item2=gsub('___.+', '', item2, perl=T)) %>%
		ggplot(aes(correlation, item2, fill=item1)) + 
		geom_col() +
		scale_y_reordered() +
		facet_wrap(~item1, scale='free_y')

        gglist <- list(gpairs_by_columns_dataset, gpairs_by_others, rmat, pmat, unlist(corr_graph_scatters_list))

        
return(gglist)
}

```


#  TOTALS IN TORRANCE
## ANALYSES BY PERCENTILE
## Notes:
- Check "elaboracion" variable 
- Three children above 30


```{r, percentil_torrance_paired_correlations_graph, echo=FALSE}
percgglist <- col_graphic_paired_significant_corrs(torrance_percentil, sign=0.05)
percgglist[[1]]
```
### Grouped by Temperament, Raven and Other Variables

```{r, percentil_other_variables_paired_correlations_graph, echo=FALSE}
percgglist[[2]]
```


```{r, duplicateprint_corr_matrix}
#print(gglist[[3]])
```
```{r, duplicateprint_pvalues_matrix}
#print(gglist[[4]])
```

# Correlation Matrix
## Notas
- Only Marginaly significant, p < 0.1, correlations
#  P-values Matrix
All p-values 
```{r}
gglist <- col_graphic_paired_significant_corrs(torrance_totals, sign=0.10)
```

```{r, print_corr_matrix}
#print(gglist[[3]])
```
```{r, print_pvalues_matrix}
#print(gglist[[4]])
```

## GRAPHICS PAIRED CORRELATIONS
### Grouped by Totals in Torrance

```{r, totals_torrance_paired_correlations_graph, echo=FALSE}
gglist[[1]]
```
### Grouped by Temperament, Raven and Other Variables

```{r, other_variables_paired_correlations_graph, echo=FALSE}
gglist[[2]]
```

