---
title: 'ANOVAs Variables Categoricas'
subtitle: 'Analisis por Grupos de Percentiles y por Escuela, Grupo, Sexo, Dx etc.'
author: 'Ma Fernanda Serrano'
date: 2022-09-06
tags: ['anova', 'categorical', 'variables categoricas', 'Fer Serrano', 'Torrance']
toc: TRUE
toc_depth: 3
output: hugodown::md_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
#source('https://github.com/umontano/CBQ_comandos_SPSS_lab_ChyC/raw/main/correlation_graphics.R')
source('https://github.com/umontano/CBQ_comandos_SPSS_lab_ChyC/raw/main/CBQ_comandosSPSS_lab_CHyC.R')
#source('https://github.com/umontano/ferserrano/raw/main/categoric.R')
source('/a/ferserrano/categoric.R')
```

# Significant differences among groups
## Divided by percentiles
- Two groups above and below-equal median (75 percentile)
- Three groups with 66 and 86 percentiles

### Percentile-groups Differences in Raven
```{r, raven_percgroups_multi_lm_graph, warning = FALSE}
raven_names <- c('percentil', 'rango', 'columna_a', 'columna_ab', 'columna_b', 'puntaje')
#RAVEN
rrrr <- merged_lm_responses_to_predictors(raven, torrance_groups_perc, raven_names, threshold_significance = 0.05, categorical_flag = FALSE)
```

### Percentile-groups Differences in Subdimensions
```{r, subdims_percgroups_multi_lm_graph, warning = FALSE}
#SUBDIMESIONS
rrrr <- merged_lm_responses_to_predictors(scales, torrance_groups_perc, threshold_significance = 0.05, categorical_flag = FALSE)
```

### Percentile-groups Differences in the three broad dimensions
```{r, dims_percgroups_multi_lm_graph, warning = FALSE}
#DIMESIONS
rrrr <- merged_lm_responses_to_predictors(factors, torrance_groups_perc, c('CE', 'AN', 'SU'), threshold_significance = 0.05, categorical_flag = FALSE)
```


# Results from Analysis of Differences Among Groups
- Categorical Variables are used as predictors
- Torrance Numeric Variables are used as responses

## Torrance Percentiles

```{r, percentile_torrance_multi_lm_graph, warning = FALSE}
#using torrance partial variabels generate lm list
perctor_categorical <- merged_categorical_and_torrance_totals(torrance_percentil)
#partial torrance varisables sent to lm_mapped
perctor_results <- merged_lm_responses_to_predictors(perctor_categorical[[1]], perctor_categorical[[2]], threshold_significance = 0.05, categorical_flag = FALSE)
```

## Torrance Partials
```{r, partials_torrance_multi_lm_graph, warning = FALSE}
#using torrance partial variabels generate lm list
partor_categorical <- merged_categorical_and_torrance_totals(torrance)
#partial torrance varisables sent to lm_mapped
partialtor_results <- merged_lm_responses_to_predictors(partor_categorical[[1]],partor_categorical[[2]], threshold_significance = 0.05, categorical_flag = FALSE)
#partialtor_results <- send_responses_to_predictors_lm(partor_categorical[[1]], partor_categorical[[2]], 0.05, TRUE)
```

## Torrance Totals (Aggregated Variables)
- Only marginally significant, p < 0.06, differences
```{r, totals_torrance_multi_lm_graph, warning = FALSE}
#generate list of responses_torrancetorals and predictors_categorical for lm
tor_categorical <- merged_categorical_and_torrance_totals(torrance_totals)
#Send list to lm_mapped function
categorical_results <- merged_lm_responses_to_predictors(tor_categorical[[1]],tor_categorical[[2]], threshold_significance = 0.06, categorical_flag = FALSE)
#categorical_results <- send_responses_to_predictors_lm(tor_categorical[[1]], tor_categorical[[2]], 0.05, TRUE)
```
