---
#TEST 02 GIT
title: "Exploratory Factor Analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}

#LOAD DATA
raw_information <- read.csv('https://raw.githubusercontent.com/Laboratorio-CHyC/Temperament/main/cbqLab_serrano2022.csv' , header=TRUE )
#CORRE EL SCRIPT con datos MAFER-SERRANO+VALE+KAREN (CBQ COMANDOS SPSS)
source('https://raw.githubusercontent.com/umontano/CBQ_comandos_SPSS_lab_ChyC/main/CBQ_SIN_INVERTIR_vale_karen_mfserrano.R')
       
```

# CRONBACH'S ALPHA AND FACTOR ANALYSIS
```{r}
source('https://raw.githubusercontent.com/umontano/CBQ_comandos_SPSS_lab_ChyC/main/CBQ_alpha_mfserrano_vale_karen.R')
res1 <- alpha_cbq(items)
```

# ALPHA IMPARES
```{r}
items_impares <- items[seq_along(items[,1])%%2 != 0  ,]
res2 <- alpha_cbq(items_impares)
```

\pagebreak

# ALPHA PARES
```{r}
items_pares <- items[seq_along(items[,1])%%2 == 0  ,]
res3 <- alpha_cbq(items_pares)
```

\pagebreak
```{r}

restot <- data.frame(res1, res2, res3)
print(restot)
write.csv(restot, 'xCBQ_raw_alphas_todos.csv')

```

\pagebreak

=== ====================
=== ====================
=== ====================
=== ====================
=== ====================

\pagebreak

# FACTOR ANALYSIS
3 Factor Model Analysis 

## TWO FACTORS
```{r}
source('https://raw.githubusercontent.com/umontano/CBQ_comandos_SPSS_lab_ChyC/main/factor_analysis_graph_function.R')
complet  <- dimensions_noextras_att
fa_graphics(complet, 2, 0.40)
```

\pagebreak

## FOUR FACTORS
```{r}
fa_graphics(complet, 4, 0.40)
```

\pagebreak

Contributions to 3 factors.
# ANALISIS CON DATOS COMPLETOS
### PROBLEMS IN PER, STH (SPERCEPTUAL, SOOTHABILITY)
### HIGH CORRELATION BETWEEN  F1 F3, ALTHOUGH LOWER THAN VALE'S
```{r}
fa_graphics(complet, 3, 0.40)
```

\pagebreak

# ANALISIS DE DATOS DE KAREN 
```{r}
karen <- dimensions_noextras_att %>% dplyr::filter(grepl('kw1', rownames(dimensions_noextras_att)))
fa_graphics(karen, 2, 0.40)
fa_graphics(karen, 4, 0.40)
fa_graphics(karen, 3, 0.40)
```
\pagebreak

# ANALISIS DE DATOS DE VALE
### PROBLEMS IN  PER=PERCEPTUALSENSITVITY
### HIGH CORRELATION BETWEEN F1 F3 
```{r}
vale <- dimensions_noextras_att %>% dplyr::filter(grepl('vm0', rownames(dimensions_noextras_att)))
fa_graphics(vale, 2, 0.40)
fa_graphics(vale, 4, 0.40)
fa_graphics(vale, 3, 0.40)
```
