---
title: "Exploratory Factor Analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

3 Factor Model Analysis 

```{r, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(broom)

```

```{r, include=FALSE}
#CORRE EL SCRIPT con datos MAFER-SERRANO+VALE+KAREN (CBQ COMANDOS SPSS)
source('https://raw.githubusercontent.com/umontano/CBQ_comandos_SPSS_lab_ChyC/main/CBQ_SIN_INVERTIDOS_lab_CHyC.R')
```

# CRONBACH'S ALPHA AND FACTOR ANALYSIS
```{r}
source('https://raw.githubusercontent.com/umontano/CBQ_comandos_SPSS_lab_ChyC/main/CBQ_alpha_mfserrano_vale_karen.R')
```

# ALPHA IMPARES
```{r}
items_impares <- items[seq_along(items[,1])%%2 != 0  ,]
alpha_cbq(items_impares)
```

# ALPHA PARES
```{r}
items_pares <- items[seq_along(items[,1])%%2 == 0  ,]
alpha_cbq(items_pares)
```

=== ====================
=== ====================
=== ====================
=== ====================
=== ====================
# FACTOR ANALYSIS
## TWO FACTORS
```{r}
source('~/u/temperament_ant_vale_karen_mfserrano/factor_analysis_graph_function.R')
complet  <- dimensions_noextras_att
fa_graphics(complet, 2, 0.40)
```

## FOUR FACTORS
```{r}
fa_graphics(complet, 4, 0.40)
```

Contributions to 3 factors.
# ANALISIS CON DATOS COMPLETOS
### PROBLEMS IN PER, STH (SPERCEPTUAL, SOOTHABILITY)
### HIGH CORRELATION BETWEEN  F1 F3, ALTHOUGH LOWER THAN VALE'S
```{r}
fa_graphics(complet, 3, 0.40)
```

# ANALISIS DE DATOS DE KAREN 
```{r}
karen <- dimensions_noextras_att %>% dplyr::filter(grepl('kw1', rownames(dimensions_noextras_att)))
fa_graphics(karen, 2, 0.40)
fa_graphics(karen, 4, 0.40)
fa_graphics(karen, 3, 0.40)
```

# ANALISIS DE DATOS DE VALE
### PROBLEMS IN  PER=PERCEPTUALSENSITVITY
### HIGH CORRELATION BETWEEN F1 F3 
```{r}
vale <- dimensions_noextras_att %>% dplyr::filter(grepl('vm0', rownames(dimensions_noextras_att)))
fa_graphics(vale, 2, 0.40)
fa_graphics(vale, 4, 0.40)
fa_graphics(vale, 3, 0.40)
```
