---
title: "NO ATTSHI NO ATTCON (ATTFOC ONLY), Factor Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
#CORRE EL SCRIPT con datos SIN INVERTIR de MAFER-SERRANO+VALE+KAREN
source('https://raw.githubusercontent.com/umontano/CBQ_comandos_SPSS_lab_ChyC/main/CBQ_SIN_INVERTIDOS_lab_CHyC.R')
```

=== ====================
=== ====================
=== ====================
=== ====================
=== ====================
# FACTOR ANALYSIS
3 Factor Model Analysis 

## TWO FACTORS
```{r, echo=FALSE}
source('https://raw.githubusercontent.com/umontano/CBQ_comandos_SPSS_lab_ChyC/main/factor_analysis_graph_function.R')
library(tidyr)
library(broom)
library(ggplot2)
#complet  <- dimensions_noextras_att
library(dplyr)

complet <- scales %>%
       select(-attshi, -attcon)

fa_graphics(complet, 2, 0.40)
```

\pagebreak

## FOUR FACTORS
```{r, echo=FALSE}
fa_graphics(complet, 4, 0.40)
```

\pagebreak

Contributions to 3 factors.
# ANALISIS CON DATOS COMPLETOS
### PROBLEMS IN PER, STH (SPERCEPTUAL, SOOTHABILITY)
### HIGH CORRELATION BETWEEN  F1 F3, ALTHOUGH LOWER THAN VALE'S
```{r, echo=FALSE}
fa_graphics(complet, 3, 0.40)
```

\pagebreak

# ANALISIS DE DATOS DE KAREN 
```{r, echo=FALSE}
karen <- complet %>% dplyr::filter(grepl('kw1', rownames(complet)))
fa_graphics(karen, 2, 0.40)
fa_graphics(karen, 4, 0.40)
fa_graphics(karen, 3, 0.40)
```
\pagebreak

# ANALISIS DE DATOS DE VALE
### PROBLEMS IN  PER=PERCEPTUALSENSITVITY
### HIGH CORRELATION BETWEEN F1 F3 

```{r, echo=FALSE}
vale <- complet %>% dplyr::filter(grepl('vm0', rownames(complet)))
fa_graphics(vale, 2, 0.40)
fa_graphics(vale, 4, 0.40)
fa_graphics(vale, 3, 0.40)
```
