---
title: " grit, Esfuerzo,  Preocupacion"
author: "Ma. Fernanda Serrano"
date: 2024-04-10
tags: ["descriptivo", "altas capacidades", "numeric variables", "Fer Serrano", "tenacidad", "perfeccionismo"]
output: hugodown::md_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
#https://github.com/Mafer-sg/Altas-Capacidades.git
## RUN DATASET WRANGLING AND COMPUTATIONS.
source('https://github.com/Mafer-sg/Altas-Capacidades/raw/main/tenacidad.R')
## LOAD DESCRIPTIVE GRAPHICS FUNCTIONS.
source('https://github.com/umontano/analysis/raw/main/boxbar.R')
```


# SCORE MEANS AND SD TABLES
These are the tables containing the mean and SD.

- GRIT
- Esfuerzo
- Preocupacion

Tables with the default formatting for publication on scientific journals.
```{r, percent_beautiful_tables}
knitr::kable(list_by_school_mean_sd_tables[[1]], caption = 'PIDAHI', digits = 1)
knitr::kable(list_by_school_mean_sd_tables[[2]], caption = 'Congreso', digits = 1)
knitr::kable(list_by_school_mean_sd_tables[[3]], caption = 'Augusto', digits = 1)
```

# LEVEL PERCENTAGE TABLES.
Tables containing the distribution of subjets in the corresponding level profiles.
```{r, score_means_sd_beautiful_tables}
knitr::kable(list_extracted_levels_datasets[[1]][[1]], caption = 'Tenacidad: Pocentaje Niveles', digits = 1)
knitr::kable(list_extracted_levels_datasets[[1]][[2]], caption = 'Esfuerzo', digits = 1)
knitr::kable(list_extracted_levels_datasets[[1]][[3]], caption = 'Tenacidad', digits = 1)
knitr::kable(list_extracted_levels_datasets[[2]][[1]], caption = 'Tenacidad', digits = 1)
knitr::kable(list_extracted_levels_datasets[[2]][[2]], caption = 'Tenacidad', digits = 1)
knitr::kable(list_extracted_levels_datasets[[2]][[3]], caption = 'Tenacidad', digits = 1)
knitr::kable(list_extracted_levels_datasets[[3]][[1]], caption = 'Tenacidad', digits = 1)
knitr::kable(list_extracted_levels_datasets[[3]][[2]], caption = 'Tenacidad', digits = 1)
knitr::kable(list_extracted_levels_datasets[[3]][[3]], caption = 'Tenacidad', digits = 1)
```

# PERCENTAGE GRAPHICS
```{r, percent_graphics}
list_by_school_levels_percents_tables
```


## EXAMPLES OF HOW TO EXTRACT ITEMS FROM LISTS
The levels percents tables are list of 3x3x2 with school names, level name and table/graph keys.
The means table is a 3 items list with school name keys.

- list_by_school_levels_percents_tables[['secaugusto']][['preocupacion_level']][['table']]

- list_by_school_mean_sd_tables[['secaugusto']]





# STACKED BARS FOR LEVELS OF EMPF AND GRIT
```{r, dodge, echo = FALSE, warning = FALSE, message = FALSE}
## VERSION DODGE
barplots_list <- bars_multicat_multicat_mapped(levels_grit_esfuer_preoc, categorical_info, 'dodge')
# SHOW PLOTS
barplots_list[[1]]
barplots_list[[2]]
barplots_list[[3]]
```

## GRIT, ESFUERZO AND PREOCUPACION, PROPORTION VERSION.
```{r, proportions, echo = FALSE, warning = FALSE, message = FALSE}
barplots_list <- bars_multicat_multicat_mapped(levels_grit_esfuer_preoc, categorical_info, 'fill')
# SHOW PLOTS
barplots_list[[1]]
barplots_list[[2]]
barplots_list[[3]]
```

## BOXPLOTS GRIT
```{r,tenacidad_grit, echo = FALSE, warning = FALSE, message = FALSE}
#boxplots_takes_1numeric_many_categoricals(grit_means, categorical_info)

## COMPUTE USING LAPPLY WITH MULTINUM AND MULTICAT DATAFRAMES
plots_list <- boxplots_multinum_multicat_mapped(scores_grit_esfuer_preoc, categorical_info)
## SHOW FIRT PLOT IN LIST
print(plots_list[[1]])
```

## BOXPLOTS EMPF
```{r, esfuerzo_boxplots, echo = FALSE, warning = FALSE, message = FALSE}
## THE SINGLE NUMERICAL COLUM FUNCTION IS
#boxplots_takes_1numeric_many_categoricals(empf_means, categorical_info)

## SHOW SECOND PLOT IN LIST
plots_list[[2]]
```

```{r, preocupacion_boxplots}
plots_list[[3]]
```
