---
title: " grit, Esfuerzo,  Preocupacion"
author: "Ma. Fernanda Serrano"
date: 2024-04-10
tags: ["descriptivo", "altas capacidades", "numeric variables", "Fer Serrano", "tenacidad", "perfeccionismo"]
output: hugodown::md_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
## RUN DATASET WRANGLING AND COMPUTATIONS.
source('https://github.com/Mafer-sg/Altas-Capacidades/raw/main/tenacidad.R')

## LOAD DESCRIPTIVE GRAPHICS FUNCTIONS.
source('https://github.com/umontano/analysis/raw/main/boxbar.R')
#https://github.com/Mafer-sg/Altas-Capacidades.git
```

# SCORE MEANS AND SD TABLES
These are the resulting tables containing the mean and sd for:

- GRIT
- Esfuerzo
- Preocupacion

## PUBLICATION READY _OR BEAUTIFUL_ TABLES
Tables with the default formatting for publication on scientific journals.

```{r, beautiful_tables}
library(gt)
list_beauty_tables_meansd <- lapply(list_by_school_mean_sd_tables, gt)
list_beauty_tables_levels <- lapply(list_by_school_levels_percents_tables, function(each_school) {

## extract list of tables
list_beauty_tables_levels
list_beauty_tables_meansd
```

## EXAMPLES OF HOW TO EXTRACT ITEMS FROM LISTS
The levels percents tables are list of 3x3x2 with school names, level name and table/graph keys.
The means table is a 3 items list with school name keys.

- list_by_school_levels_percents_tables[['secaugusto']][['preocupacion_level']][['table']]

- list_by_school_mean_sd_tables[['secaugusto']]

```{r, score_means_sd_tables}
print(list_by_school_mean_sd_tables)
```


# PROFILE  LEVELS
Results profiles and levels.

## TABLES BY SCHOOLS. RAW VERSION
These are the tables containting the percentages of subjects under each level.

```{r, tables_school_grade}
print(list_by_school_levels_percents_tables)
```
# NUMERIC RESULTS

## MEANS AND LEVELS EMPF AND GRIT
```{r}
print('==GRIT SD==:')
head(scores_grit_esfuer_preoc)
head(levels_grit_esfuer_preoc)
```

## STACKED BARS FOR LEVELS OF EMPF AND GRIT
```{r, dodge, echo = FALSE, warning = FALSE, message = FALSE}
## VERSION DODGE
barplots_list <- bars_multicat_multicat_mapped(levels_grit_esfuer_preoc, categorical_info, 'dodge')
# SHOW PLOTS
barplots_list[[1]]
barplots_list[[2]]
barplots_list[[3]]
```

## GRIT, ESFUERZO AND PREOCUPACION, PROPORTION VERSION.
```{r, proportions, echo = FALSE, warning = FALSE, message = FALSE}
barplots_list <- bars_multicat_multicat_mapped(levels_grit_esfuer_preoc, categorical_info, 'fill')
# SHOW PLOTS
barplots_list[[1]]
barplots_list[[2]]
barplots_list[[3]]
```

## BOXPLOTS GRIT
```{r,tenacidad_grit, echo = FALSE, warning = FALSE, message = FALSE}
#boxplots_takes_1numeric_many_categoricals(grit_means, categorical_info)

## COMPUTE USING LAPPLY WITH MULTINUM AND MULTICAT DATAFRAMES
plots_list <- boxplots_multinum_multicat_mapped(scores_grit_esfuer_preoc, categorical_info)
## SHOW FIRT PLOT IN LIST
print(plots_list[[1]])
```

## BOXPLOTS EMPF
```{r, empf, echo = FALSE, warning = FALSE, message = FALSE}
## THE SINGLE NUMERICAL COLUM FUNCTION IS
#boxplots_takes_1numeric_many_categoricals(empf_means, categorical_info)

## SHOW SECOND PLOT IN LIST
plots_list[[2]]
```

```{r}
plots_list[[3]]
```
